Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2018-12-31 ms5n17-tlp-mn-180216-001.tex
wording changes 3

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}
The spectra in \fig{fig:lineshape} and \fig{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse. Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}.

@@

Initially FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
showed inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing (not shown).
To avoid these inhomogeneities and therefore to achieve better resolution, 
detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
and takes longer to obtain compared to FR4. 
It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
once the design has been validated.

@@

The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons. 
\fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
No signs of arcing were obseved at this power level for pulses up to 1~ms duration.

@@

Figure~\ref{fig:HSQC} shows the possibility of useful double resonance experiments in the current setup. On left, $^{13}$C-$^{1}$H-HSQC spectrum, acquired in 12 mins (32 t$_1$ increments and 16 scans) from 2.5 $\mu$l sample of 100 mM $^{13}$C-glucose dissolved in water. On right, $^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in a buffer solution. $^{15}$N is a very insensitive nuclei hence very difficult to detect. $^{15}$N-$^{1}$H-HSQC spectrum on 1 mM of protein sample clearly shows that the current probe can be used for protein structure studies with minimal amount of isotopically labeled protein.\par
\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec} 
\end{figure}
\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
\caption{$^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T. Glucose HSQC spectrum was acquired in 12 minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400 minutes from a 1 mM sample.}
\label{fig:HSQC} 
\end{figure}
The probe has been used to make micro MR (magnetic resonance) images using a Bruker imaging unit. Figure~\ref{fig:tisli} shows MR images of mouse liver tissue slice immersed in DMEM cell growth media acquired by putting the slices in a microfluidic device with circular sample chamber to accommodate the slice. The acquisition times for MR images were 1 minute, 25 minutes and 8 minutes for gradient echo, spin echo and RARE 8 (rapid acquisition with relaxation enhancement) respectively. Though the commercial imaging unit is optimised for bigger sample size (30 mm inner diameter max), images with in-plane resolution of 30 ($\mu$m)$^{2}$ are recorded for a 3 mm liver slice of thickness 300~$\mu$m. Here we have presented preliminary results of imaging experiments. In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.\par
\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
\caption{MR images of a freshly cut live slice from a mouse. A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: magnetic field map; D Spin echo image acquired in 30 minutes; E: RARE8 image acquired in 8 minutes.}
\label{fig:tisli} 
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
We have presented a novel modular NMR probe assembly for generic high sensitivity microfluidic NMR experiments. The probe is built from the readily accessible materials with no requirement of parts from commercial probes. The modularity of the probe enables to use different detectors tailored for specific experimental requirements on the same probe skeleton. The detector is made from easily available PCB materials. The use of PCB allows to modify the probe circuit and design without disturbing the probe geometry. The probe has excellent B$_1$ homogeneity and sensitivity. The resolution is reasonable for primary metabolic studies but needs to be improved for generic applications. The probe has already been used for various diverse experiments like reaction monitoring, protein structure determination, micro-imaging of mouse liver tissue slices, metabolic studies of mammalian cells, hyperpolarisation on the chip etc. Although in the current form the probe can be used for generic 2D experiments, in the future we intend to include extra channels for lock and pulses on other nuclei. Though, commercial gradient system has been successful to make micro images of mouse liver tissue slices, a dedicated gradient system can be included on the probe PCB for shimming and imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}
This research was funded through "Future and Emerging Technologies" (FETOPEN) call of the EU Horizon 2020 research framework. Authors would like to thank William Hale and Bishnubrata Patra for making microfluidic devices and Dr. Katrin Deinhardt from Department of Biological Science at UoS, for the mouse liver tissue..
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{unsrt}
\bibliography{science}
\end{document}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Discussion}

@@

Initially, FR4 PCB material was used for the detector assembly because of its low cost and easy availability. 
B$_0$ field maps of the sample chamber obtained from gradient echo images using these detectors 
showed inhomogeneities in the B$_0$ field due to the glass fibre rovings in FR4's composite backing (not shown).
To avoid these inhomogeneities and therefore to achieve better resolution, 
detectors were made from RO3035 material. While RO3035 provides better resolution, it is more expensive 
and takes longer to obtain compared to FR4. 
It therefore makes sense to first prototype new detector designs in FR4, and only use the more expensive RO3035 
once the design has been validated.

@@

The probe is not sensitive enough to make direct detection of $^{15}$N signals practical. Nutation at the
$^{15}$N frequency was therefore detected indirectly using coherence transfer to protons \cite{bax_indirect}. 
\fig{fig:15N-nutation} shows the results. Using 100~W of input power \todo{verify power setting} 
produces nutation frequencies of 6 kHz for $^{15}$N and 14 kHz for $^{13}$C. 
No signs of arcing were obseved at this power level for pulses up to 1~ms duration.

@@

Figure~\ref{fig:HSQC} demonstrates proton-detected double resonance experiments in the current setup. 
The left panel shows a $^{13}$C-$^{1}$H heteronuclear single quantum correlation (HSQC) spectrum, acquired in 12 mins 
(32 t$_1$ increments and 16 scans) 
from a 2.5 $\mu$l sample of 100 mM u-$^{13}$C-glucose dissolved in water. The right panel shows a 
$^{15}$N-$^{1}$H-HSQC spectrum, acquired in 400 mins (64 t$_1$ increments and 128 scans) 
from 2.5 $\mu$l sample of 1 mM $^{15}$N-ubiquitin (17 $\mu$g) dissolved in 10 mM phosphate buffer at pH 7. 
All expected cross peaks are present in the spectrum. The ability to obtain meaningful  \textsuperscript{1}H-
\textsuperscript{15}N correlation spectra from such small samples could prove very useful in the context of
proteins that are difficult to express and therefore only available in small quantities. The integration of
protein NMR and microfluidic technology also opens new possibilities for high-throughput kinetics and 
binding studies.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 
\caption{Spectrum of culture growth media recorded in 256 scans with water presaturation. The total experimental time was 20 min for 2.5 $\mu$l sample volume.}
\label{fig:media-spec} 
\end{figure}

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 
\caption{ $^1$H-$^{13}$C HSQC spectrum of $^{13}$C labeled glucose (left) and $^1$H-$^{15}$N HSQC of $^{15}$N labeled Ubiquitin (right) both acquired from 2.5$\mu$l sample volume at 14 T. Glucose HSQC spectrum was acquired in 12 minutes from a 100 mM sample. Ubiquitin HSQC spectrum was acquired in 400 minutes from a 1 mM sample.}
\label{fig:HSQC} 
\end{figure}

The probe can also be used to make micro MR (magnetic resonance) images using a Bruker micro-gradient  unit. 
To this effect, the aluminium probe sleeve must be replaced by an electrically insulating material in order to 
avoid image distortions due to eddy currents in the sleeve. 
Figure~\ref{fig:tisli} shows MR images of mouse liver tissue slice 
immersed in DMEM cell growth medium.
The slice was placed in a microfluidic device with circular sample chamber centred at the detector location, as 
shown in \fig{fig:tisli}A. 
The image shown in \fig{fig:tisli}B was acquired using a gradient echo (FLASH) pulse sequence with repetion time
$t_R=120$~ms and echo time $t_E=12$~ms \todo{verify all values}
The acquisition times for MR images were 1 minute, 25 minutes and 8 minutes for gradient echo, spin echo and RARE 8 (rapid acquisition with relaxation enhancement) respectively. Though the commercial imaging unit is optimised for bigger sample size (30 mm inner diameter max), images with in-plane resolution of 30 ($\mu$m)$^{2}$ are recorded for a 3 mm liver slice of thickness 300~$\mu$m. Here we have presented preliminary results of imaging experiments. In future we aim to include a dedicated micro-imaging setup for better resolution to make metabolic profile maps by diffusion tensor imaging.

\begin{figure}
\centering
\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 
\caption{MR images of a freshly cut live slice from a mouse. A: optical micrograph; B: Gradient echo image acquired in 1 minute; C: magnetic field map; D Spin echo image acquired in 30 minutes; E: RARE8 image acquired in 8 minutes.}
\label{fig:tisli} 
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
We have presented a novel modular NMR probe assembly for generic high sensitivity microfluidic NMR experiments. The probe is built from the readily accessible materials with no requirement of parts from commercial probes. The modularity of the probe enables to use different detectors tailored for specific experimental requirements on the same probe skeleton. The detector is made from easily available PCB materials. The use of PCB allows to modify the probe circuit and design without disturbing the probe geometry. The probe has excellent B$_1$ homogeneity and sensitivity. The resolution is reasonable for primary metabolic studies but needs to be improved for generic applications. The probe has already been used for various diverse experiments like reaction monitoring, protein structure determination, micro-imaging of mouse liver tissue slices, metabolic studies of mammalian cells, hyperpolarisation on the chip etc. Although in the current form the probe can be used for generic 2D experiments, in the future we intend to include extra channels for lock and pulses on other nuclei. Though, commercial gradient system has been successful to make micro images of mouse liver tissue slices, a dedicated gradient system can be included on the probe PCB for shimming and imaging.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}
This research was funded through "Future and Emerging Technologies" (FETOPEN) call of the EU Horizon 2020 research framework. Authors would like to thank William Hale and Bishnubrata Patra for making microfluidic devices and Dr. Katrin Deinhardt from Department of Biological Science at UoS, for the mouse liver tissue..
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\bibliographystyle{unsrt}
\bibliography{science}
\end{document}
